---
title: "Country Level Automated Report for `r params$country`"
output: html_document
params:
  country: "DefaultCountry" # This default value is just for testing
---
## General Information ##

Within this report we have country-specific categorical descriptive statistics. We can observe each report is a stand-alone document (take note of the 100% percentage of the specified state, along with the frequency of reports, and then a break down by category comprising the entire frequency). Our continuous variable, age, is also state-specific. Then we display bar charts on responses by sex regarding our two dependent variables; jobs_are_scarce and child_suffers. Last we show a regression model along with a dynamic report explaining the results. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(stargazer)
library(purrr)
library(kableExtra)

load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df1c.RData")
load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df2c.RData")
load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df3c.RData")
```

```{r filter-data, include=FALSE}

# Assuming df1c is already loaded
country_data <- df1c %>%
  filter(country == params$country)

```


## Table 1 - Categorical Variable Descriptive Statistics ##
```{r load-data, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE)

load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df1c.RData")

# Filter df1c for the specified country
country_specific_df1c <- df1c %>% filter(country == params$country)


calculate_frequencies <- function(data, var_name) {
  data %>%
    count(!!sym(var_name), name = "Frequency") %>%
    mutate(Percentage = Frequency / sum(Frequency) * 100,
           Category = as.character(!!sym(var_name)),
           Variable = var_name) %>%
    select(Variable, Category, Frequency, Percentage)
}

load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df1c.RData")
# List of categorical variables
categorical_vars <- c("country", "education", "child_suffers", "jobs_are_scarce")

# Calculate frequencies and percentages for each variable and bind rows together
load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df1c.RData")
categorical_summary <- map_dfr(categorical_vars, ~calculate_frequencies(df1c, .x))


# Assuming calculate_frequencies function is defined as before
categorical_summary_country <- map_dfr(categorical_vars, ~calculate_frequencies(country_data, .x))

knitr::kable(categorical_summary_country, booktabs = TRUE, caption = paste("Descriptive Summary of Categorical Variables for", params$country)) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm")


``` 
## Table 2 - Continuous Variable Descriptive Statistics ##
```{r continous, message=FALSE, echo=FALSE}
load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df1c.RData")

# Filter df1c for the specified country
country_specific_df1c <- df1c %>% filter(country == params$country)


# Ensure you're using the filtered data for the specific country
country_data <- country_data %>%
  mutate(age = ifelse(age >= 82, 82, age)) %>%
  mutate(age = as.numeric(age),  # Attempt to convert age to numeric
         age = ifelse(is.na(age), NA, age))  # Convert non-numeric to NA

# Now calculate descriptive statistics using the country-specific data
country_data %>%
  summarise(
    Mean = mean(age, na.rm = TRUE),
    SD = sd(age, na.rm = TRUE),
    Min = min(age, na.rm = TRUE),
    `25% Quantile` = quantile(age, 0.25, na.rm = TRUE),
    Median = median(age, na.rm = TRUE),
    `75% Quantile` = quantile(age, 0.75, na.rm = TRUE),
    Max = max(age, na.rm = TRUE)
  ) %>%
  knitr::kable(caption = paste("Descriptive Statistics for Age in", params$country))
```
# Sex Impact on Dependent Variables #

### Plot 1 Sex/Jobs are Scarce ###
```{r jobs-are-scarce-bar-plot, echo=FALSE, fig.width=14, fig.height=6}
library(ggplot2)

#  filtered dataset for the specific country
# This step is necessary to apply the country filter correctly for each report
country_data <- country_data %>%
  mutate(jobs_are_scarce = as.factor(jobs_are_scarce),
         respondent_sex = as.factor(respondent_sex))

# Create a bar plot
ggplot(country_data, aes(x = jobs_are_scarce, fill = respondent_sex)) +
  geom_bar(position = "dodge") + # Use "dodge" to place bars side by side
  labs(title = paste("Response to Jobs Are Scarce by Sex in", params$country),
       x = "Jobs Are Scarce Response", y = "Count") +
  scale_fill_brewer(palette = "Set1", name = "Sex") + # Optional: Use a color palette
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Improve x-axis label readability
```

### Plot 2 Sex/Child Suffers ###

```{r child-suffers-sex-bar-plot, echo=FALSE, fig.width=14, fig.height=6}
library(ggplot2)

# Make sure to use the country-specific filtered dataset
country_data <- country_data %>%
  mutate(child_suffers = as.factor(child_suffers),
         respondent_sex = as.factor(respondent_sex))

# Create a bar plot for "child suffers" responses by sex
ggplot(country_data, aes(x = child_suffers, fill = respondent_sex)) +
  geom_bar(position = "dodge") + # Bars side by side for clarity
  labs(title = paste("Responses to Child Suffers by Sex in", params$country),
       x = "Child Suffers Response", y = "Count") +
  scale_fill_brewer(palette = "Set1", name = "Sex") + # Color differentiation
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Adjust for readability
```

## Regression Models ##

```{r regression-results-and-table, echo=FALSE, results='asis'}
# Load the data
load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df2c.RData")
load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df3c.RData")
# Filter df3c for the specified country
df3c <- df3c %>% filter(country == params$country)
# Ensure 'respondent_sex' is treated as a factor for modeling
df2c$respondent_sex <- as.factor(df2c$respondent_sex)

# Optionally, ensure numeric encoding is correct for 'respondent_sex' if not already
#df2c$respondent_sex <- relevel(df2c$respondent_sex, ref = "male") # Adjust based on your data

# Fit the model for "jobs_are_scarce_numeric"
model_jobs <- lm(jobs_are_scarce_numeric ~ respondent_sex, data = df2c)

# Fit the model for "child_suffers_numeric"
model_child <- lm(child_suffers_numeric ~ respondent_sex, data = df2c)

# Dynamic interpretation for jobs_are_scarce_numeric model
coef_summary_jobs <- summary(model_jobs)$coefficients
sex_effect_jobs <- coef_summary_jobs["respondent_sexfemale", ] # Adjust based on your coding

# Check if the coefficient is statistically significant for jobs model
significant_jobs <- ifelse(sex_effect_jobs[4] < 0.05, "statistically significant", "not statistically significant")

interpretation_jobs <- paste(" For 'jobs_are_scarce_numeric', in the context of ", params$country, ", the effect of the sex variable shows a ",
                        ifelse(sex_effect_jobs[1] > 0, "positive", "negative"), 
                        " relationship with a coefficient of ", round(sex_effect_jobs[1], 3), 
                        ". This relationship is ", significant_jobs, ".", sep = "")

cat(interpretation_jobs)

# Dynamic interpretation for child_suffers_numeric model
coef_summary_child <- summary(model_child)$coefficients
sex_effect_child <- coef_summary_child["respondent_sexfemale", ] # Adjust based on your coding

# Check if the coefficient is statistically significant for child model
significant_child <- ifelse(sex_effect_child[4] < 0.05, "statistically significant", "not statistically significant")

interpretation_child <- paste(" For 'child_suffers_numeric', in the context of ", params$country, ", the effect of the sex variable shows a ",
                        ifelse(sex_effect_child[1] > 0, "positive", "negative"), 
                        " relationship with a coefficient of ", round(sex_effect_child[1], 3), 
                        ". This relationship is ", significant_child, ".", sep = "")

cat(interpretation_child)
```

```{r echo=FALSE, results='asis'}
 stargazer(model_child, model_jobs, type = "html",
            title = paste("Regression Models for", params$country),
            out.header = FALSE, model.names = FALSE,
            covariate.labels = c("Intercept", "Sex"))

```

