---
title: "HW R Markdown"
author: "Chris Rice"
date: "2024-03-09"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=TRUE}
library(dplyr)
library(purrr) # Make sure to load purrr
library(knitr)
library(kableExtra)

```


---
title: "EVS 2017 Data Review"
output: pdf_document
---
According to the [website](https://search.gesis.org/research_data/ZA7500#variables|exploredata-ZA7500_Varv72|0|variable_order|asc): *The European Values Study is a large-scale, cross-national and longitudinal survey research program on how Europeans think about family, work, religion, politics, and society. Repeated every nine years in an increasing number of countries, the survey provides insights into the ideas, beliefs, preferences, attitudes, values, and opinions of citizens all over Europe.*

Beginning steps were to create an account with the aforementioned website in order to extract either the SPSS or STATA file. In this case, we downloaded the STATA file in order to create an EVS 2017 analysis. Specific variables of this project's interest were as follows:  

1. Respondent's age (continuous)
2. Respondent's country (categorical)
3. Respondent's education (categorical)
4. Respondent's sex (categorical)
5. Respondent's opinion on if jobs are scarce should national citizens have priority over immigrants (categorical)
6. Respondent's opinion on if a child suffers when the mother is working (categorical)


## Table 1 - Categorical Variable Descriptive Statistics ##
```{r load-data, message=FALSE}
load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df1c.RData")

calculate_frequencies <- function(data, var_name) {
  data %>%
    count(!!sym(var_name), name = "Frequency") %>%
    mutate(Percentage = Frequency / sum(Frequency) * 100,
           Category = as.character(!!sym(var_name)),
           Variable = var_name) %>%
    select(Variable, Category, Frequency, Percentage)
}

load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df1c.RData")
# List of categorical variables
categorical_vars <- c("country", "education", "child_suffers", "jobs_are_scarce")

# Calculate frequencies and percentages for each variable and bind rows together
load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df1c.RData")
categorical_summary <- map_dfr(categorical_vars, ~calculate_frequencies(df1c, .x))

# Display the table
load("C:/Users/ricecakes/Desktop/Git1/HW-2/Rcode/df1c.RData")
knitr::kable(categorical_summary, booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm")
``` 
## Table 2 - Continuous Variable Descriptive Statistics 
```{r continous, message=FALSE}
df1c <- df1c %>%
  mutate(age = ifelse(age >= 82, 82, age))


df1c <- df1c %>%
  mutate(age = as.numeric(age),  # Attempt to convert age to numeric
         age = ifelse(is.na(age), NA, age))  # Non-numeric become NA


df1c %>%
  summarise(
    Mean = mean(age, na.rm = TRUE),
    SD = sd(age, na.rm = TRUE),
    Min = min(age, na.rm = TRUE),
    `25% Quantile` = quantile(age, 0.25, na.rm = TRUE),
    Median = median(age, na.rm = TRUE),
    `75% Quantile` = quantile(age, 0.75, na.rm = TRUE),
    Max = max(age, na.rm = TRUE)
  ) %>%
  knitr::kable()  

```
### No NAs in "age" confirmed ###
```{r}
 unique(df1c$age)


```
## How the 2 Vars of interest change with age (jobs_are_scare/child_suffers) ##
### jobs_are_scarce with age ###
Enter words here when ready
```{r categorical-table, echo=TRUE, fig.width=14, fig.height=6}
library(ggplot2)
df1c <- df1c %>%
  mutate(jobs_are_scarce = as.factor(jobs_are_scarce))


ggplot(df1c, aes(x = jobs_are_scarce, y = age)) +
  geom_violin(trim = FALSE) +
  geom_boxplot(width = 0.1, fill = "white") +  # Adding a narrow boxplot inside for median/quartiles
  labs(title = "Age Distribution by Jobs Are Scarce Response",
       x = "Jobs Are Scarce Response",
       y = "Age") +
  theme_minimal()

```

### child_suffers with age ###

Enter words here for dialogue

```{r child-suffers-age, echo=TRUE, fig.width=14, fig.height=6}

library(ggplot2)

# Ensure 'child_suffers' is treated as a factor
df1c <- df1c %>%
  mutate(child_suffers = as.factor(child_suffers))

# Plotting the relationship between 'child_suffers' responses and 'age'
ggplot(df1c, aes(x = child_suffers, y = age)) +
  geom_violin(trim = FALSE) +
  geom_boxplot(width = 0.1, fill = "white") +  # Adding a narrow boxplot inside for median/quartiles
  labs(title = "Age Distribution by Child Suffers Response",
       x = "Child Suffers Response",
       y = "Age") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  #  
```

## Regression Models ##



```{r}
library(dplyr)
library(stargazer)

df1c <- df1c %>%
  mutate(age_squared = age^2,
         respondent_sex = as.factor(respondent_sex),
         education = as.factor(education))

model1 <- lm(jobs_are_scarce ~ age + age_squared + respondent_sex + education, data = df1c)
model2 <- lm(child_suffers ~ age + age_squared + respondent_sex + education, data = df1c)

stargazer(model1, model2, type = "text", 
          title = "Regression Models Results",
          align = TRUE,
          header = FALSE,
          model.numbers = FALSE)


```

